### 2024-06-04 thesis/input_files/literaturereview.tex
cleaned all problems and warnings

%Electricity Forecasting 
%intro
During the past 25 years %because paper of 2014 says 15, so now it is 25
a wide range of new ideas have been proposed for electricity point forecasting and for probabilistic forecasting.
\\
The field benefitted greatly from the increase of computing power, the greater availability of data and the interest in data science.
As a consequence, the forecaster's toolbox has grown in size and complexity.
\\
Before delving into the literature review, we stress that at this point in time there is no superior method. Different solutions may outperform or underperform compared to other techniques depending on the problem settings. Thus, understanding the complexity, strengths and weaknesses of each method is crucial for fitting the right model to the right setting.
\\
Within this research community, the need for more homogeneity in the choice of the error valuation metrics emerged (Section \ref{metrics}), data quality and in the way of comparing model performances \cite{EPF_review}. As a solution, \cite{lago} proposes a checklist to aid evaluating the meaningfulness of new research. Throughout this thesis work, we will stick to the proposed principles and best practices peculiar of the EF field.
%literature review

\section{Electricity forecasting classification}
Electricity forecasting is a vague term and is used in the literature to refer to the whole field. Thus, in order to introduce some clarity, it is useful to classify the range of EF articles in terms of their core attributes.
\\
In the context of energy forecasting, the quantities of most interest are electricity prices (EPF), electricity loads (ELF) and renewables generation (mostly wind and solar).
\\
In terms of forecasting horizons, we can group EF into four major categories: very short term forecasting (VSTF), short term forecasting (STF), medium term forecasting (MTF) and long term forecasting (LTF). Consensus in the literature is to use one day, two weeks and three years respectively as cut off horizons \cite{hong_phd}; see Figure \ref{fig:time} for a visualisation. 
\begin{figure}
  \includegraphics[width=\textwidth]{images/time_2.png}
  \caption{Time classification \cite{prob_elf}}
  \label{fig:time}
\end{figure}
\\
Forecasts can either be for the whole target electricity network (system) or for a subset of it (zonal).
\\
EF literature distinguishes between point and probabilistic forecasts. Each of the two has its advantages and disadvantages. Point forecasts are easier to generate and less computationally intensive while probabilistic forecasts are more informative. Industry and research efforts have focused primarily on point forecasting. Nevertheless, interest in probabilistic forecasting has risen considerably over the last years due to renewable integration requirements, introduction of smart grids and increased market competitiveness.
\section{Bibliographic analysis}
This section presents the results of the bibliometric analysis we performed on March $6^{th}$ 2024. This survey has been carried out by using the Scopus citation database. For details on the specific queries entered in Scopus, refer to Appendix \ref{src_code}.
\\
To get started, let us consider the evolution of the EF field over the years. This is visualised in Figure \ref{fig:epf_evolution}, with results grouped by category. Articles prior to the 2000 have been aggregated together due to their small number. Figure \ref{fig:epf_evolution} shows the trend of an increasing interest in EF.
\begin{figure}
    \includegraphics[width=\textwidth]{images/epf_evolution1.jpg}
    \caption{Electricity forecasting publications over the past years}
    \label{fig:epf_evolution}
  \end{figure}
\\
The next question is to compare the state of point-versus probabilistic forecasting, this is visualised in Figure \ref{fig:point_vs_prob}. What can be concluded is that probabilistic-is less developed than point forecasting. To our mind this is due to the complexity of probabilistic forecasts.
Nevertheless, we can see a trend that suggests researchers are making an effort to fill this gap.
\begin{figure}
  \includegraphics[width=\textwidth]{images/point_vs_prob.jpg}
  \caption{Point versus probabilistic publications over the past years}
  \label{fig:point_vs_prob}
\end{figure}
\\
The EF literature is dominated by statistical-and computational intelligence (CI) methods as can be seen from Figure \ref{fig:cs_stat_both}, with CI methods being slightly preferred. 
\begin{figure}
  \includegraphics[width=\textwidth]{images/cs_stat_both.jpg}
  \caption{Publications by method over the past years}
  \label{fig:cs_stat_both}
\end{figure}
\\
EF is a heterogeneous field of research, its researchers come from a wide array of backgrounds, with electrical engineers and statisticians making up the top contributors; their different educational training may explain why the split between statistical and computational intelligence methods is so marked. Figure \ref{fig:subject_area} depicts the EF publications by subject area. What can be concluded is that the bulk of publications come from engineering, computer science, mathematics and econometrics.
\begin{figure}
  \includegraphics[width=\textwidth]{images/subject_area.png}
  \caption{Publications by subject area}
  \label{fig:subject_area}
\end{figure}
\\
In order to refer to the most relevant source in the field, EF outlets have been ranked by popularity and plotted in Figure \ref{fig:src_title}.
\begin{figure}
  \includegraphics[width=\textwidth]{images/src_title.png}
  \caption{Most popular sources/outlets}
  \label{fig:src_title}
\end{figure}
\\

@@

\\

@@

\\
%GEFCom2012
A major step forward in EF was the creation of the global energy forecasting competition (GEFCom) in 2012. Until then, no formal benchmarking process or data pool was established and new publications rarely reproduced the results from work done by others. Addressing these issues was the motivation behind the creation of GEFCom by the IEEE working group on energy forecasting. The EF field was positively affected by this competition. A number of ideas were tested on the same setting with only the best ones being published and it also contributed bridging the gap between industry practice and academic research. GEFCom2012 had two tracks; the former about hierarchical load forecasting, the latter about wind power forecasting, see \cite{hong2014global} for a comprehensive review. 
\\
%GEFCom 2014
The focus of GEFCom2014 was on probabilistic forecasting, Hong et al.\ \cite{hong2016probabilistic} discusses the problem tracks, the data and the winning methods.
In this paragraph some of the winning entries of the 2014 GEFCom edition are discussed.
Xie et al.\ \cite{xie2016gefcom2014} proposes a two stage approach; in the first stage they use multiple linear regression (MLR) to build a point forecast, then in the second stage they try different approaches for modelling the MLR residuals, among other they tried exponential smoothing (ESM), artificial neural networks (ANN) and autoregressive integrated moving average (ARIMA). 
Maciejowska et al.\ \cite{maciejowska2016hybrid} proposes a new probabilistic model extending the idea of quantile regression averaging (QRA) \cite{nowotarski2015computing}.
Haben et al.\ \cite{haben2016hybrid} mixes conditional kernel density (CKD) and quantile regression in their competition entry.
Gaillard et al.\ \cite{gaillard2016additive,gaillardasemi} combines quantile regression with generalised additive models \cite{hastie2017generalized}.
Ziel et al.\ \cite{ziel2016lasso} estimates an AR model through the LASSO \cite{tibshirani1996regression} instead of the standard OLS.
\\
%GEFCom 2017
The last GEFCom was held in 2017, its focus was providing hierarchical probabilistic load forecasts, see \cite{hong2019global}. The GEFCom competition has also inspired the organisation of other competitions such as the RWEnpower competition in the UK, the RTE competition in France, the Tokyo electric power company competition in Japan and the BigDEAL forecasting competitions.
\\
\\
A couple of considerations can be drawn from the above literature review.
The EF field is characterised by heterogeneity in its forecasting techniques; methods come from statisitics, mathematics, econometrics, electrical engineering and the artificial intelligence communities.
\\
Every paper uses different datasets.
Therefore, it is not possible to directly compare results from one paper to another without implementing the paper specific algorithms and then applying them to the respective dataset. An additional hurdle is that some datasets are not freely accessible.
\\
Thus, a good understanding of the state of the art methods in EF is required to carry out a rigorous comparison between methods.
That is why the following chapters are devoted to summarising the mathematical theory underlying such techniques.

\section{Kernel methods literature review}
%INTRO KERNEL METHODS E ENERGY PRICE MODELLING
Kernel methods are a class of algorithms for pattern analysis.
With kernel methods we are able to apply linear methods with predictors in a high dimensional space, without having to explicitly evaluate the involved dot products of the features.
Throughout this thesis, we will address the performance of kernel methods in the context of EF.
\\
%- Kernel history evolution.
Their name comes from the German word kern, which translates to core in english. Such term was first used by David Hilbert in his paper on integral equations \cite{hilbert} where he introduced the term "definite kernels". Following, Hilbert's and Schmidt's work, \cite{schmidt} lead to the introduction of a new space, the Hilbert space.
In 1909, James Mercer improved Hilbert's work by proposing his theorem \cite{mercer}. This theorem underlies the power of kernel methods, that is the kernel trick.
In 1938, Schoenberg \cite{schoenberg} developed the mathematical results that allow us to find the kernel associated to a specific feature space metric.
In 1941, Kolmogorov \cite{kolmogorov} carried out stuides on representing kernels in linear spaces.
In 1950, Aronszajn \cite{aronszajn} published the first work on reproducing kernel Hilbert spaces (RKHS); developing the general method for representing kernels in linear spaces.
In 1964, Aizerman \cite{aizerman} further improved the theory of RKHS.
It was in the 1990s that the theory of kernel methods got popular, particularly in the field of machine learning. Kernels have been used in various different tasks such as support vector machines (SVM) \cite{vapnik1} \cite{vapnik2}, Gaussian process classifiers \cite{williams}, spline methods \cite{wahba}, neural networks \cite{poggio} and principal component analysis \cite{pca_scholkopf}.
Nevertheless kernel methods received very little attention in the specific setting of EF literature.
\\
The kernel theory needed for this thesis work is covered in Section \ref{kernel_theory}. 
For an introduction to kernel methods, we refer to \cite{learning_with_kernels, hofmann2006review, shawe2004kernel}.
\\
Kanagawa et Fukumizu introduces to the concept of kernel mean embedding \cite{pmlr}. Muandet et al.\ \cite{Muandet_2017} surveys established results and new advances in the theory of Hilbert space distribution embeddings. 
It has to be said that, computing and storing such embeddings becomes prohibitive for large scale settings. Rudi et al.\ \cite{2022nystrom} proposes an efficient approximation procedure based on the Nyström method \cite{nystrom}, providing also an upper bound for the approximation error.
Another example of the applicability of kernel methods is \cite{supersamples}. In that paper, Smola et al.\ kernelize the herding algorithm introduced in \cite{welling2009herding,welling2009herding,Welling2010}. The original herding algorithm converts empirical moments into a sequence of pseudo-samples approximating the probability density function (PDF) of the observed random variable. Its weakness is that it can only take a finite number of features and this limits its expressive power.
Smola et al.\ overcome this by translating the algorithm into the framework of kernels.

>>>>

During the past 25 years a wide range of new ideas have been proposed for electricity point forecasting and for probabilistic forecasting. The field benefitted greatly from the increase of computing power, the greater availability of data and the interest in data science. As a consequence, the forecaster's toolbox has grown in size and complexity. Before delving into the literature review, we stress that at this point in time there is no superior method. Different solutions may outperform or underperform compared to other techniques depending on the problem settings. Thus, understanding the complexity, strengths and weaknesses of each method is crucial for fitting the right model to the right setting. Within this research community, the need for more homogeneity in the choice of the error valuation metrics emerged (Section \ref{metrics}), data quality and in the way of comparing model performances \cite{EPF_review}. As a solution, \cite{lago} proposes a checklist to aid evaluating the meaningfulness of new research. Throughout this thesis work, we will stick to the proposed principles and best practices peculiar of the EF field.
%literature review

\section{Electricity forecasting classification}
Electricity forecasting is a vague term and is used in the literature to refer to the whole field. Thus, in order to introduce some clarity, it is useful to classify the range of EF articles in terms of their core attributes.
In the context of energy forecasting, the quantities of most interest are electricity prices (EPF), electricity loads (ELF) and renewables generation (mostly wind and solar).
In terms of forecasting horizons, we can group EF into four major categories: very short term forecasting (VSTF), short term forecasting (STF), medium term forecasting (MTF) and long term forecasting (LTF). Consensus in the literature is to use one day, two weeks and three years respectively as cut off horizons \cite{hong_phd}; see Figure \ref{fig:time} for a visualisation. 
\begin{figure}
  \includegraphics[width=\textwidth]{images/time_2.png}
  \caption{Time classification \cite{prob_elf}}
  \label{fig:time}
\end{figure}
Forecasts can either be for the whole target electricity network (system) or for a subset of it (zonal).
EF literature distinguishes between point and probabilistic forecasts. Each of the two has its advantages and disadvantages. Point forecasts are easier to generate and less computationally intensive while probabilistic forecasts are more informative. Industry and research efforts have focused primarily on point forecasting. Nevertheless, interest in probabilistic forecasting has risen considerably over the last years due to renewable integration requirements, introduction of smart grids and increased market competitiveness.
\section{Bibliographic analysis}
This section presents the results of the bibliometric analysis we performed on March $6^{th}$ 2024. This survey has been carried out by using the Scopus citation database. For details on the specific queries entered in Scopus, refer to Appendix \ref{src_code}.

To get started, let us consider the evolution of the EF field over the years. This is visualised in Figure \ref{fig:epf_evolution}, with results grouped by category. Articles prior to the 2000 have been aggregated together due to their small number. Figure \ref{fig:epf_evolution} shows the trend of an increasing interest in EF.
\begin{figure}
    \includegraphics[width=\textwidth]{images/epf_evolution1.jpg}
    \caption{Electricity forecasting publications over the past years}
    \label{fig:epf_evolution}
  \end{figure}

The next question is to compare the state of point-versus probabilistic forecasting, this is visualised in Figure \ref{fig:point_vs_prob}. What can be concluded is that probabilistic-is less developed than point forecasting. To our mind this is due to the complexity of probabilistic forecasts.
Nevertheless, we can see a trend that suggests researchers are making an effort to fill this gap.

\begin{figure}
  \includegraphics[width=\textwidth]{images/point_vs_prob.jpg}
  \caption{Point versus probabilistic publications over the past years}
  \label{fig:point_vs_prob}
\end{figure}

The EF literature is dominated by statistical-and computational intelligence (CI) methods as can be seen from Figure \ref{fig:cs_stat_both}, with CI methods being slightly preferred. 
\begin{figure}
  \includegraphics[width=\textwidth]{images/cs_stat_both.jpg}
  \caption{Publications by method over the past years}
  \label{fig:cs_stat_both}
\end{figure}

EF is a heterogeneous field of research, its researchers come from a wide array of backgrounds, with electrical engineers and statisticians making up the top contributors; their different educational training may explain why the split between statistical and computational intelligence methods is so marked. Figure \ref{fig:subject_area} depicts the EF publications by subject area. What can be concluded is that the bulk of publications come from engineering, computer science, mathematics and econometrics.
\begin{figure}
  \includegraphics[width=\textwidth]{images/subject_area.png}
  \caption{Publications by subject area}
  \label{fig:subject_area}
\end{figure}

In order to refer to the most relevant source in the field, EF outlets have been ranked by popularity and plotted in Figure \ref{fig:src_title}.
\begin{figure}
  \includegraphics[width=\textwidth]{images/src_title.png}
  \caption{Most popular sources/outlets}
  \label{fig:src_title}
\end{figure}

@@

@@

%GEFCom2012
A major step forward in EF was the creation of the global energy forecasting competition (GEFCom) in 2012. Until then, no formal benchmarking process or data pool was established and new publications rarely reproduced the results from work done by others. Addressing these issues was the motivation behind the creation of GEFCom by the IEEE working group on energy forecasting. The EF field was positively affected by this competition. A number of ideas were tested on the same setting with only the best ones being published and it also contributed bridging the gap between industry practice and academic research. GEFCom2012 had two tracks; the former about hierarchical load forecasting, the latter about wind power forecasting, see \cite{hong2014global} for a comprehensive review. 
%GEFCom 2014
The focus of GEFCom2014 was on probabilistic forecasting, Hong et al.\ \cite{hong2016probabilistic} discusses the problem tracks, the data and the winning methods.
In this paragraph some of the winning entries of the 2014 GEFCom edition are discussed.
Xie et al.\ \cite{xie2016gefcom2014} proposes a two stage approach; in the first stage they use multiple linear regression (MLR) to build a point forecast, then in the second stage they try different approaches for modelling the MLR residuals, among other they tried exponential smoothing (ESM), artificial neural networks (ANN) and autoregressive integrated moving average (ARIMA). 
Maciejowska et al.\ \cite{maciejowska2016hybrid} proposes a new probabilistic model extending the idea of quantile regression averaging (QRA) \cite{nowotarski2015computing}.
Haben et al.\ \cite{haben2016hybrid} mixes conditional kernel density (CKD) and quantile regression in their competition entry.
Gaillard et al.\ \cite{gaillard2016additive,gaillardasemi} combines quantile regression with generalised additive models \cite{hastie2017generalized}.
Ziel et al.\ \cite{ziel2016lasso} estimates an AR model through the LASSO \cite{tibshirani1996regression} instead of the standard OLS.
%GEFCom 2017
The last GEFCom was held in 2017, its focus was providing hierarchical probabilistic load forecasts, see \cite{hong2019global}. The GEFCom competition has also inspired the organisation of other competitions such as the RWEnpower competition in the UK, the RTE competition in France, the Tokyo electric power company competition in Japan and the BigDEAL forecasting competitions.

A couple of considerations can be drawn from the above literature review.
The EF field is characterised by heterogeneity in its forecasting techniques; methods come from statisitics, mathematics, econometrics, electrical engineering and the artificial intelligence communities.
Every paper uses different datasets.
Therefore, it is not possible to directly compare results from one paper to another without implementing the paper specific algorithms and then applying them to the respective dataset. An additional hurdle is that some datasets are not freely accessible.
Thus, a good understanding of the state of the art methods in EF is required to carry out a rigorous comparison between methods.
That is why the following chapters are devoted to summarising the mathematical theory underlying such techniques.

\section{Kernel methods literature review}
%INTRO KERNEL METHODS E ENERGY PRICE MODELLING
Kernel methods are a class of algorithms for pattern analysis.
With kernel methods we are able to apply linear methods with predictors in a high dimensional space, without having to explicitly evaluate the involved dot products of the features.
Throughout this thesis, we will address the performance of kernel methods in the context of EF.

%- Kernel history evolution.
Their name comes from the German word kern, which translates to core in english. Such term was first used by David Hilbert in his paper on integral equations \cite{hilbert} where he introduced the term "definite kernels". Following, Hilbert's and Schmidt's work, \cite{schmidt} lead to the introduction of a new space, the Hilbert space.
In 1909, James Mercer improved Hilbert's work by proposing his theorem \cite{mercer}. This theorem underlies the power of kernel methods, that is the kernel trick.
In 1938, Schoenberg \cite{schoenberg} developed the mathematical results that allow us to find the kernel associated to a specific feature space metric.
In 1941, Kolmogorov \cite{kolmogorov} carried out stuides on representing kernels in linear spaces.
In 1950, Aronszajn \cite{aronszajn} published the first work on reproducing kernel Hilbert spaces (RKHS); developing the general method for representing kernels in linear spaces.
In 1964, Aizerman \cite{aizerman} further improved the theory of RKHS.
It was in the 1990s that the theory of kernel methods got popular, particularly in the field of machine learning. Kernels have been used in various different tasks such as support vector machines (SVM) \cite{vapnik1} \cite{vapnik2}, Gaussian process classifiers \cite{williams}, spline methods \cite{wahba}, neural networks \cite{poggio} and principal component analysis \cite{pca_scholkopf}.
Nevertheless kernel methods received very little attention in the specific setting of EF literature.

The kernel theory needed for this thesis work is covered in Section \ref{kernel_theory}. 
For an introduction to kernel methods, we refer to \cite{learning_with_kernels, hofmann2006review, shawe2004kernel}.

Kanagawa et Fukumizu introduces to the concept of kernel mean embedding \cite{pmlr}. Muandet et al.\ \cite{Muandet_2017} surveys established results and new advances in the theory of Hilbert space distribution embeddings. 
It has to be said that, computing and storing such embeddings becomes prohibitive for large scale settings. Rudi et al.\ \cite{2022nystrom} proposes an efficient approximation procedure based on the Nyström method \cite{nystrom}, providing also an upper bound for the approximation error.
Another example of the applicability of kernel methods is \cite{supersamples}. In that paper, Smola et al.\ kernelize the herding algorithm introduced in \cite{welling2009herding,welling2009herding,Welling2010}. The original herding algorithm converts empirical moments into a sequence of pseudo-samples approximating the probability density function (PDF) of the observed random variable. Its weakness is that it can only take a finite number of features and this limits its expressive power.
Smola et al.\ overcome this by translating the algorithm into the framework of kernels.

### 2024-06-04 thesis/input_files/metrics.tex
cleaned all problems and warnings

\section{Pinball score}\label{pinball}
The pinball score or quantile score is used to measure the accuracy of a quantile forecast.
\begin{definition}
    The pinball loss is defined as
    $$
    \mathrm{Pinball}(y_{t},\hat{y}_{t,q},q)=
\begin{cases}
(q-1)(\hat{y}_{t,q}-y_{t}) & y_t > \hat{y}_{t,q} \\
q(\hat{y}_{t,q}-y_t) & y_t \leq \hat{y}_{t,q}
\end{cases}
$$
\end{definition}
The pinball loss is an asymmetric function, it weights its score differently depending on the error sign and on the quantile considered, see Figure \ref{fig:pinball}.
\begin{figure}
    \includegraphics[width=\textwidth]{images/pinball_loss.png}
    \caption{Pinball loss}
    \label{fig:pinball}
  \end{figure}
By averaging all the pinball losses over all quantiles and over the whole forecast horizon, we obtain the pinball loss of the probabilistic forecast.
\section{Winkler score}
\begin{definition}
    The Winkler score is defined as
    $$
    \mathrm{Winkler}(y_t,  u_{t},l_{t},\alpha)=\begin{cases}
        \delta & l_{t}\leq y_{t}\leq u_{t}\\
        \delta+2(l_{t}-y_{t})/\alpha & y_{t}< l_{t}\\
        \delta+2(l_{t}-u_{t})/\alpha & y_{t} \geq u_{t}
    \end{cases}
    $$
\end{definition}
Where $\delta$ is the prediction interval (PI) width, that is $\delta=u_t-l_t$, $\alpha$ is (1-coverage level), $u_t$ is the prediction interval upper threshold and $l_t$ is the prediction interval lower threshold at time step $t$. This score penalises observations falling outside the prediction interval and rewards narrow prediction intervals.
\section{Continous ranked probability score}
The continous ranked probability score (CRPS) measures the difference between the estimated cumulative distribution $\hat{F}$ and the empirical cumulative density function (CDF).
\begin{definition}\label{def_crps}
    The continous ranked probability score is defined as
    $$
    \mathrm{CRPS}(y, \hat{F})=\int\limits_{-\infty}^{\infty}\left(\hat{F}(x)-\mathbb{I}_{\{x-y\}} \right)^2 dx
    $$
\end{definition}
% Nevertheless, we can evaluate the integral in closed form. 
Where the indicator function is defined as 
    $$\mathbb{I}_{\{z\}}=
\begin{cases}
0, & z<0\\
1, & z \geq 0
\end{cases}$$
\\
For a visualisation see Figure \ref{fig:crps}. The grey area is what contributes toward the CRPS score.
The better the estimated cumulative density function is the smaller the total CRPS score will be.
\begin{figure}
    \includegraphics[width=\textwidth]{images/crps.png}
    \caption{CRPS integral \cite{haben2023core}}
    \label{fig:crps}
  \end{figure}
  \\
It is worth noting, that the CRPS integral can be rewritten in terms of expectations. This makes its evaluation easier, since we know that the sample mean converges to the expectation for sufficiently big sample sizes by the law of large numbers. This was first pointed out by \cite{proper_scores}, where the authors take advantage of Lemma 2.2 of \cite{new_multi_test2} or equivalently identity (17) of \cite{new_multi_tes1}.
\\
\begin{lemma}
    Let $X_1$, $X_2$, $Y_1$, $Y_2$ be independent real random variables with finite expectations. Let $X_1,X_2$ be identically distributed with distribution function $F$ and let $Y_1,Y_2$ be identically distributed with distribution function $G$. Then
   \begin{equation}\label{eq:crps_expectation}
    \mathbb{E}(|X_1-Y_1|)-\frac{1}{2}\mathbb{E}(|X_1-X_2|)-\frac{1}{2}\mathbb{E}(|Y_1-Y_2|)=\int\limits_{-\infty}^{\infty}\left(F(x)-G(x)\right)^2dx
\end{equation}
\end{lemma}
Notice that, in our case, Equation \ref{eq:crps_expectation}, the distribution $G$ of $Y_1$ and $Y_2$ is degenerate, with all probability mass on a single point $y$.
%  (x notation will need to be cleaned here). Since $G(t)=:$
It follows that the third addend in the summation is zero. That is because $Y_1$ and $Y_2$ both following distribution $G$ implies that $\mathbb{E}(|Y_1-Y_2|)$ corresponds to the difference of two equal constant numbers.
\\

@@

\\
Putting everything together we have obtained an alternative way of computing the CRPS score.
\begin{equation}
    \int\limits_{-\infty}^{\infty}\left(\hat{F}(x)-\mathbb{I}_{\{x-y\}} \right)^2 dx=\mathbb{E}(|X_1-y|)-\frac{1}{2}\mathbb{E}(|X_1-X_2|)
\end{equation}
\\
\section{Probability integral transform}
The probability integral transform (PIT) is a method to assess visually the quality of a probabilistic forecast. PIT is obtained by applying the predicted cumulative density function $\hat{F}$ to the data. If applying such CDF to the data results in a uniform distributed PIT, then $\hat{F}$ is a valid prediction. If not, $\hat{F}$ is not a good estimate of the CDF for the considered data. Figure \ref{fig:pit} provides an example, applying the true CDF results in a well calibrated PIT (left). Alternatively, applying a bad CDF results in either an overdispersed (middle) or underdispersed (right) PIT.
\begin{figure}
    \includegraphics[width=\textwidth]{images/pit.png}
    \caption{Probability integral transform types \cite{haben2023core}}
    \label{fig:pit}
  \end{figure}
\\
%RELIABILITY PLOT
%PICP,NMPIW,CWC,unconditional coverage(arora)-->Probability density forecasting of wind speed based on quantile regression and kernel density estimation Lei Zhang

>>>>

\section{Pinball score}\label{pinball}
The pinball score or quantile score is used to measure the accuracy of a quantile forecast.
\begin{definition}
    The pinball loss is defined as
    $$
    \mathrm{Pinball}(y_{t},\hat{y}_{t,q},q)=
\begin{cases}
(q-1)(\hat{y}_{t,q}-y_{t}) & y_t > \hat{y}_{t,q} \\
q(\hat{y}_{t,q}-y_t) & y_t \leq \hat{y}_{t,q}
\end{cases}
$$
\end{definition}
The pinball loss is an asymmetric function, it weights its score differently depending on the error sign and on the quantile considered, see Figure \ref{fig:pinball}.
\begin{figure}
    \includegraphics[width=\textwidth]{images/pinball_loss.png}
    \caption{Pinball loss}
    \label{fig:pinball}
  \end{figure}
By averaging all the pinball losses over all quantiles and over the whole forecast horizon, we obtain the pinball loss of the probabilistic forecast.
\section{Winkler score}
\begin{definition}
    The Winkler score is defined as
    $$
    \mathrm{Winkler}(y_t,  u_{t},l_{t},\alpha)=\begin{cases}
        \delta & l_{t}\leq y_{t}\leq u_{t}\\
        \delta+2(l_{t}-y_{t})/\alpha & y_{t}< l_{t}\\
        \delta+2(l_{t}-u_{t})/\alpha & y_{t} \geq u_{t}
    \end{cases}
    $$
\end{definition}
Where $\delta$ is the prediction interval (PI) width, that is $\delta=u_t-l_t$, $\alpha$ is (1-coverage level), $u_t$ is the prediction interval upper threshold and $l_t$ is the prediction interval lower threshold at time step $t$. This score penalises observations falling outside the prediction interval and rewards narrow prediction intervals.
\section{Continous ranked probability score}
The continous ranked probability score (CRPS) measures the difference between the estimated cumulative distribution $\hat{F}$ and the empirical cumulative density function (CDF).
\begin{definition}\label{def_crps}
    The continous ranked probability score is defined as
    $$
    \mathrm{CRPS}(y, \hat{F})=\int\limits_{-\infty}^{\infty}\left(\hat{F}(x)-\mathbb{I}_{\{x-y\}} \right)^2 dx
    $$
\end{definition}
% Nevertheless, we can evaluate the integral in closed form. 
Where the indicator function is defined as 
    $$\mathbb{I}_{\{z\}}=
\begin{cases}
0, & z<0\\
1, & z \geq 0
\end{cases}$$
\\
For a visualisation see Figure \ref{fig:crps}. The grey area is what contributes toward the CRPS score.
The better the estimated cumulative density function is the smaller the total CRPS score will be.
\begin{figure}
    \includegraphics[width=\textwidth]{images/crps.png}
    \caption{CRPS integral \cite{haben2023core}}
    \label{fig:crps}
  \end{figure}
It is worth noting, that the CRPS integral can be rewritten in terms of expectations. This makes its evaluation easier, since we know that the sample mean converges to the expectation for sufficiently big sample sizes by the law of large numbers. This was first pointed out by \cite{proper_scores}, where the authors take advantage of Lemma 2.2 of \cite{new_multi_test2} or equivalently identity (17) of \cite{new_multi_tes1}.
\\
\begin{lemma}
    Let $X_1$, $X_2$, $Y_1$, $Y_2$ be independent real random variables with finite expectations. Let $X_1,X_2$ be identically distributed with distribution function $F$ and let $Y_1,Y_2$ be identically distributed with distribution function $G$. Then
   \begin{equation}\label{eq:crps_expectation}
    \mathbb{E}(|X_1-Y_1|)-\frac{1}{2}\mathbb{E}(|X_1-X_2|)-\frac{1}{2}\mathbb{E}(|Y_1-Y_2|)=\int\limits_{-\infty}^{\infty}\left(F(x)-G(x)\right)^2dx
\end{equation}
\end{lemma}
Notice that, in our case, Equation \ref{eq:crps_expectation}, the distribution $G$ of $Y_1$ and $Y_2$ is degenerate, with all probability mass on a single point $y$.
%  (x notation will need to be cleaned here). Since $G(t)=:$
It follows that the third addend in the summation is zero. That is because $Y_1$ and $Y_2$ both following distribution $G$ implies that $\mathbb{E}(|Y_1-Y_2|)$ corresponds to the difference of two equal constant numbers.

@@

Putting everything together we have obtained an alternative way of computing the CRPS score.
\begin{equation}
    \int\limits_{-\infty}^{\infty}\left(\hat{F}(x)-\mathbb{I}_{\{x-y\}} \right)^2 dx=\mathbb{E}(|X_1-y|)-\frac{1}{2}\mathbb{E}(|X_1-X_2|)
\end{equation}

\section{Probability integral transform}
The probability integral transform (PIT) is a method to assess visually the quality of a probabilistic forecast. PIT is obtained by applying the predicted cumulative density function $\hat{F}$ to the data. If applying such CDF to the data results in a uniform distributed PIT, then $\hat{F}$ is a valid prediction. If not, $\hat{F}$ is not a good estimate of the CDF for the considered data. Figure \ref{fig:pit} provides an example, applying the true CDF results in a well calibrated PIT (left). Alternatively, applying a bad CDF results in either an overdispersed (middle) or underdispersed (right) PIT.
\begin{figure}
    \includegraphics[width=\textwidth]{images/pit.png}
    \caption{Probability integral transform types \cite{haben2023core}}
    \label{fig:pit}
  \end{figure}

%RELIABILITY PLOT
%PICP,NMPIW,CWC,unconditional coverage(arora)-->Probability density forecasting of wind speed based on quantile regression and kernel density estimation Lei Zhang
